Calculating Biological Module Enrichment or Depletion and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}

### 2016-01-22 jss/article.tex
[skip ci] update ACK

%% almost as usual
\author{Paul Deveau\\Institut Curie\\PSL Research University\\Univ. Paris-Sud\\INSERM U830\\INSERM U900\\Mines-ParisTech \And 
        Eric Bonnet\\Institut Curie\\PSL Research University\\INSERM U900\\Mines-ParisTech}
\title{Calculating Biological Module Enrichment or Depletion and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Paul Deveau, Eric Bonnet} %% comma-separated
\Plaintitle{Calculating Biological Module Enrichment or Depletion and Visualizing Data on Large-scale Molecular Maps with the R packages ACSNMineR and RNaviCell} %% without formatting
\Shorttitle{Module Enrichment and Data Visualization with ACSNMineR and RNaviCell} %% a short title (if necessary)

@@

The authors would like to thank Pierre Gestraud for his comments on early
versions of the \pkg{ACSNMineR} package and Eric Viara for guidance and
assistance on the development of the \pkg{RNaviCell} package.

>>>>

%% almost as usual
\author{Paul Deveau\\Institut Curie\\PSL University\\Univ. Paris-Sud\\INSERM U830\\INSERM U900\\Mines-ParisTech \And 
        Emmanuel Barillot\\Institut Curie\\PSL University\\INSERM U900\\Mines-ParisTech \And 
        Andrei Zinovyev\\Institut Curie\\PSL University\\INSERM U900\\Mines-ParisTech \And
        Eric Bonnet\\Institut Curie\\PSL University\\INSERM U900\\Mines-ParisTech}
\title{Calculating Biological Module Enrichment or Depletion and Visualizing Data on Large-scale Molecular Maps with the R packages \pkg{ACSNMineR} and \pkg{RNaviCell}}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Paul Deveau, Emmanuel Barillot, Andrei Zinovyev, Eric Bonnet} %% comma-separated
\Plaintitle{Calculating Biological Module Enrichment or Depletion and Visualizing Data on Large-scale Molecular Maps with the R packages ACSNMineR and RNaviCell} %% without formatting
\Shorttitle{Module Enrichment and Data Visualization with ACSNMineR and RNaviCell} %% a short title (if necessary)

@@

This work was supported by a grant ``Projet Incitatif et Collaboratif
Computational Systems Biology Approach for Cancer" from Institut Curie. The
authors would like to thank Pierre Gestraud for his comments on early versions
of the \pkg{ACSNMineR} package and Eric Viara for guidance and assistance on
the development of the \pkg{RNaviCell} package.
